Supplementary Materials

### 2019-01-28 sup_mat/sup_mat.Rmd
fixed some of the plots
Made plots clearer with more developed captions

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_meanrt_opt
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```

@@

```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Switch Rate and Response Times (seconds) for each participant accross conditions", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
# again, what sort of plots are we interester in?

# mean RT by repetition rate? in each condition?
plt_for_sr_rt <- dat_for %>%
  na.omit() %>%
  mutate(sub_no = as.numeric(as.factor(sub_no))) %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, search_type, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, search_type) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = search_type)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom", strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt_for_sr_rt$labels$y <- "Response Time (secs)"
plt_for_sr_rt$labels$x <- "Average Repetition Rate"
plt_for_sr_rt$labels$colour <- "Search Condition"
plt_for_sr_rt

>>>>

```{r ACS_rt, fig.cap = "\\label{fig:ACS_rt_plt} Distribution of reaction times in Adaptive Choice paradigm. Optimal choice corresponds to reporting the number that was in the box with the minority colour group.", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
grid.arrange(plt_ACS_rt_opt, plt_ACS_logrt_opt)
```

```{r ACS_rt_optchoice, fig.cap = "\\label{fig:ACS_rt_opt_plt} Response Time (ms) by number of optimal choices in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_meanrt_opt
```

```{r ACS_acc, fig.cap = "\\label{fig:ACS_acc} Mean Accuracy for each Participant in the Adaptive Choice Task", echo = FALSE, warning = FALSE, message = FALSE, fig.align = "center"}
plt_ACS_mean_acc
```

@@

```{r plotting foraging, fig.cap = "\\label{fig:For_switch_rt} Average repetition rate (i.e. when the curret clicked on target is the same as the previously clicked target) and Response Times (seconds) for each participant accross conditions in the Foraging task", echo = FALSE, warnings = FALSE, message = FALSE, fig.align = "center"}
# again, what sort of plots are we interester in?

# mean RT by repetition rate? in each condition?
plt_for_sr_rt <- dat_for %>%
  na.omit() %>%
  mutate(sub_no = as.numeric(as.factor(sub_no)))

plt_for_sr_rt$Search_cond <- "Feature"
plt_for_sr_rt$Search_cond[plt_for_sr_rt$search_type == 2] <- "Conjunctive"

plt_for_sr_rt <- plt_for_sr_rt %>%
  # filter(!sub_no %in% c(27,40:43)) %>% # missing data for these participants
  group_by(sub_no, Search_cond, Trial) %>%
  mutate(RT_max = max(RT)) %>%
  group_by(sub_no, Search_cond) %>%
  summarise(mean_RT = mean(RT_max),
            mean_SW = mean(repetition)) %>%
  ggplot(aes(mean_SW, mean_RT, colour = Search_cond)) + 
  geom_point() +
  # geom_line(aes(group = sub_no), alpha = 0.3, colour = "black") + # do we want it on one plot?
  theme_bw() + 
  scale_x_continuous(breaks = c(0.5)) +
  scale_y_continuous(breaks = c(10, 30, 50)) + 
  theme(legend.position = "bottom",
        strip.text.x = element_text(margin = margin(0.01,0,0.01,0, "mm"))) +
  scale_colour_ptol() +
  facet_wrap(~sub_no)
plt_for_sr_rt$labels$y <- "Response Time (secs)"
plt_for_sr_rt$labels$x <- "Average Repetition Rate"
plt_for_sr_rt$labels$colour <- "Search Condition"
plt_for_sr_rt
